E511-Signal Processing-Final Project

### 2018-12-13 paper/main.tex
Edits from Jamie.

\subsection{Jamie's Lit Review}

@@

\section{Dataset Preparation}
\subsection{CSR-I (WSJ0) Complete}
For purposes of comparison with existing scholarship, each approach was developed based on a mixture of audio extracted from the WSJ0 dataset, a corpus of read speech texts drawn from articles in the Wall Street Journal. WSJ0 \cite{garofolo:wsj0} consists of over 35,000 audio samples organized into training and evaluation data sets organized by speaker and gender. The audio files are stored in a format called Sphere using the Shorten compression algorithm. The Linguistic Data Consortium website hosts a small utility called sph2pipe \cite{ldc:sph2pipe} which we used to convert the files from the Sphere format to waveform format. We wrote a small script to automate this process and also to merge the separate disks of the WSJ0 dataset into a single folder.

@@

\section{Speech Separation Algorithms}
\subsection{KMeans}
The technique of speaker diarization relies on a big pipeline with following steps:
\begin{itemize}
    \item Feature Extraction
    \item Speaker segmentation
    \item Speaker Clustering
    \item Evaluation
\end{itemize}
\subsubsection{Feature Extraction}
In this project, we used 3 approaches to extract features:
\begin{itemize}
    \item A chroma vector (Wikipedia) (FMP, p. 123) is a typically a 12-element feature vector indicating how much energy of each pitch class, {C, C\#, D, D\#, E, ..., B}, is present in the signal. Then use mean of each element as one of input for clustering.
    \item The mel frequency cepstral coefficients (MFCCs) of a signal are a small set of features  which concisely describe the overall shape of a spectral envelope. In this case, mfcc computed 13 MFCCs.The very first MFCC, the 0th coefficient, does not convey information relevant to the overall shape of the spectrum. It only conveys a constant offset, i.e. adding a constant value to the entire spectrum. Therefore, here I discard the first MFCC, then I scale the MFCCs such that each coefficient dimension has zero mean and unit variance.Then use mean of MFCCS as one part of input for clustering.
    \item We divide the audio signal into smaller frames. In smaller time scales audio signals are statistically unchanged. Then for each smaller frames we compute the power spectrum of the signal, and use it as the third part of input for clustering.
\end{itemize}
\subsubsection{Speaker segmentation}\cite{Segmentation} Speaker segmentation which is also known as acoustic change detection aims to detect speaker change such that each contiguous segment corresponds to single speaker only. To find if the two segments correspond to same speaker we have to define some notion of distance metric. In this case, I skipped this step and used the features extrated from above steps as input for kmeans clustering.
\subsubsection{Kmeans Clustering}
Since we knew that the audio from call center is the conversation between 2 speakers(customer service and customer), we set k=2 for kmeans clustering.\\
here it is the results for speaker diarization.
\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans01.png} 
\end{figure}

\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans02.png}
\end{figure}
\subsubsection{Evaluation\cite{Segmentation}}Diarization Error Rate (DER) is used for evaluation of automatic speech recognition system.Contribution to DER comes from three factors namely, Missed speech rate (MSR), False alarm speech rate (FASR) and Speaker Error. When a speech is labeled as non-speech then that error comes under MSR. FASR is when a non- speech is detected as a speech segment. Speaker error is contributed due to speaker clustering and segmentation. This kind of error can be caused if a speaker change is not detected, oversegmentation, erroneously clustered. Sum of all three errors contribute to the DER.\\
In this case, we don't have any labeled data to calculate the training error, we just simply used human ears to justify whether the diarization was good or not. For some training data, it works well, but some training data, it performed really bad.

@@

With the NMF method, we were unable to generate a substantial separation between the original isolated signal and the mixed audio. Both IMR approaches produced substantially better results with the cIMR method proving to be the best method for this type of separation on a consistent basis [Figure \ref{tab:masking_snr}].

\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:Comparison of Average SNR for Masking Methods 1}Comparison of Average SNR for Masking Methods}  
    \includegraphics[width=0.3\textwidth]{Mask_Res.png}  
\end{figure}

\begin{table}[h]
    \centering
    \begin{tabular}{r r r}
        Label &Waveform & Kurtosis \\

        \midrule
        0 & s.wav & 7.29 \\
        1 & x1.wav & 4.91 \\
        2 & x2.wav & 3.87 \\
        \midrule
    \end{tabular}
    \caption{Table Caption}
    \label{tab:masking_snr}
\end{table}

>>>>

\subsection{Signal Approximation}

There are several approaches to speech separation based on the general concept that audio can be represented as the combination of a frequency matrix and a corresponding matrix temporal activations. Approach the the task as a supervised learning problem,  can be used to create a masking

@@

\section{Dataset Preparation}
\subsection{CSR-I (WSJ0) Complete}
For purposes of comparison with existing scholarship, each approach was developed based on a mixture of audio extracted from the WSJ0 dataset, a corpus of read speech texts drawn from articles in the Wall Street Journal. WSJ0 \cite{garofolo:wsj0} consists of over 35,000 audio samples organized into training and evaluation data sets organized by speaker and gender. The audio files are stored in a format called Sphere using the Shorten compression algorithm. The Linguistic Data Consortium website provides a small utility called sph2pipe \cite{ldc:sph2pipe} which we used to convert the files from the Sphere format to waveform format. We wrote a small script to automate this process and also to merge the separate disks of the WSJ0 dataset into a single folder.

@@

\section{Speech Separation Algorithms}
\subsection{KMeans}
The technique of speaker diarization relies on a big pipeline with following steps:
\begin{itemize}
    \item Feature Extraction
    \item Speaker segmentation
    \item Speaker Clustering
    \item Evaluation
\end{itemize}
\subsubsection{Feature Extraction}
In this project, we used 3 approaches to extract features:
\begin{itemize}
    \item A chroma vector (Wikipedia) (FMP, p. 123) is a typically a 12-element feature vector indicating how much energy of each pitch class, {C, C\#, D, D\#, E, ..., B}, is present in the signal. Then use mean of each element as one of input for clustering.
    \item The mel frequency cepstral coefficients (MFCCs) of a signal are a small set of features  which concisely describe the overall shape of a spectral envelope. In this case, mfcc computed 13 MFCCs.The very first MFCC, the 0th coefficient, does not convey information relevant to the overall shape of the spectrum. It only conveys a constant offset, i.e. adding a constant value to the entire spectrum. Therefore, here I discard the first MFCC, then I scale the MFCCs such that each coefficient dimension has zero mean and unit variance.Then use mean of MFCCS as one part of input for clustering.
    \item We divide the audio signal into smaller frames. In smaller time scales audio signals are statistically unchanged. Then for each smaller frames we compute the power spectrum of the signal, and use it as the third part of input for clustering.
\end{itemize}
\subsubsection{Speaker segmentation}\cite{Segmentation} Speaker segmentation which is also known as acoustic change detection aims to detect speaker change such that each contiguous segment corresponds to single speaker only. To find if the two segments correspond to same speaker we have to define some notion of distance metric. In this case, I skipped this step and used the features extrated from above steps as input for kmeans clustering.
\subsubsection{Kmeans Clustering}
Since we knew that the audio from call center is the conversation between 2 speakers(customer service and customer), we set k=2 for kmeans clustering.\\
here it is the results for speaker diarization.
\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization 1}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans01.png} 
\end{figure}

\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization 2}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans02.png}
\end{figure}
\subsubsection{Evaluation\cite{Segmentation}}Diarization Error Rate (DER) is used for evaluation of automatic speech recognition system.Contribution to DER comes from three factors namely, Missed speech rate (MSR), False alarm speech rate (FASR) and Speaker Error. When a speech is labeled as non-speech then that error comes under MSR. FASR is when a non- speech is detected as a speech segment. Speaker error is contributed due to speaker clustering and segmentation. This kind of error can be caused if a speaker change is not detected, oversegmentation, erroneously clustered. Sum of all three errors contribute to the DER.\\
In this case, we don't have any labeled data to calculate the training error, we just simply used human ears to justify whether the diarization was good or not. For some training data, it works well, but some training data, it performed really bad.

@@

With the NMF method, we were unable to generate a substantial separation between the original isolated signal and the mixed audio. Both IMR approaches produced substantially better results with the cIMR method proving to be the best method for this type of separation on a consistent basis [Figure \ref{Fig:masking_snr}].

\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:masking_snr}Average SNR for Masking Methods}

  \begin{tabular}{r r r}\\

        Method & SNR \\
        \midrule
        NMF & 0.014 \\
        IRM & 6.380 \\
        cIRM & 15.070 \\
        \midrule
    \end{tabular}

\end{figure}
